Machine Learning Autoencoder Applied to Communication Channels

### 2019-06-17 Rapport/Article/Article.tex
Seance 06/17/2019

The denomination one-hot comes from the output vector that is usually a long vector of zeros with one element equals to one. This \textit{hot} vector element indicates which class the NN has classified the input. In this context, which message the code word refers to.

Tranformation from one-hot to messagges

Abscence of noise layer

Lower complexity of the NN

Loss function choice

Optimizer choice

Num epochs choice

Batchsize choice

>>>>

The denomination one-hot comes from the output vector which is usually a long vector of zeros with one element equals to one. This \textit{hot} vector element indicates which class the NN has classified the input. In this context, which message encoded in 256 different classes the code word refers to. Basically, a message is mapped into a class and a class only.

A straight forward consequence of this shallower NN is the number of training parameters almost three times less than the array decoder. Because of that, we could expect a lower training time. Also, we observed that the number of training epochs is substantially smaller for the one-hot decoder. It was necessary only $2^{14}$ epochs to achieve the results for the same batch size of $256$ and Adam optimizer.

Despite the NN complexity benefits of the one-hot decoder, it is required to transform the predicted vector into a message. Consequently, an additional operation is needed. To transform from a one-hot vector to a message, a ordered collection of the messages was stored in memory and the correspondent message is determined by a $argmax$ operation in the one-hot vector, which identifies which message is the most likely to have been transmitted through the channel.

The one-hot decoder was trained both with and without a noise layer. The model without a integrated channel converged faster to the solution. Tables \ref{tab:onehotdecoder} and \ref{tab:onehotdecoderTrain} resume all the training variables.
